---
title: "Assignment 3"
author: "Estefan A. Rivera López"
date: "`r format(Sys.time(), '%Y-%b-%d, %I:%M %p')`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

# R Tutorial 3

```{r}
library(ggplot2)
data("trees")
head(trees)
```

Q1. Create a histogram showing the distribution of Girth.
```{r, warning=FALSE}
ggplot(trees, aes(Girth)) + 
  geom_histogram(bins = 30, fill = "skyblue", color = "white")
```

Q2. Create a histogram showing the distribution of Volume.
```{r, warning=FALSE}
ggplot(trees, aes(Volume)) + 
  geom_histogram(bins = 30, fill = "forestgreen", color = "white")
```

Q3. Create a scatterplot showing the relationship between Girth and Volume.
```{r}
ggplot(trees, aes(Girth, Volume)) + 
  geom_point(color = "blue") +
  labs(title = "Girth vs Volume",
       x = "Girth",
       y = "volume")
```

Q4. Use the Shapiro–Wilk test to assess whether Volume is normally distributed. Report the p-value and state whether the data are normally distributed.
```{r}
shapiro.test(trees$Volume)
```
The Volume data is not distributed normally, as the p-value = 0.03 and is below 0.05.

Q5. Repeat the Shapiro–Wilk test for Girth. Report the p-value and state whether Girth is normally distributed.
```{r}
shapiro.test(trees$Girth)
```

The Girth data is normally distributed, as its p-value = 0.08, well over the 0.05 threshold.